Automatic Parallelization and Transparent Fault Tolerance

### 2016-07-12 pubs/tfp16-draft/paper.tex
Trims Mini-Haskell appendix.  Minor edits therein.

STG supports pattern matching but only in a simple form and only in
\texttt{case} expressions.  Mini-Haskell extends this to something approaching
what is found in Haskell.  Functions, including lambda expressions, may match on
all their arguments. Named functions may have multiple definitions to exhaust
the combinations of patterns in their arguments, and patterns in all contexts
(functions and case expressions) may be nested arbitrarily deep.  This feature
greatly simplifies the task of defining more complex behavior.  Without it,
each matched parameter of a function requires an additional level of nested
\texttt{case} expressions. The same is true of each level of nesting within a
single pattern.
%
Even relatively simple functions can be painful to write, such as \texttt{unzip}:
{\footnotesize
\begin{verbatim}
   unzip = FUN(list -> 
     case list of s1 { Nil -> let {res = CON( Pair nil nil)} in res;
                    Cons x xs -> case x of s2 {
                      Pair a b -> case unzip xs of s3 {
                        Pair as bs -> let {aas = CON(Cons a as);
                                           bbs = CON(Cons b bs);
                                           res = CON(Pair aas bbs)}
                                      in res }}})
\end{verbatim}}
\noindent In mini-Haskell this becomes
{\footnotesize
\begin{verbatim}
   unzip :: List (Pair a b) -> Pair (List a) (List b)
   unzip Nil = Pair Nil Nil
   unzip (Cons (Pair a b) xs) =
     case unzip xs of
       Pair as bs -> Pair (Cons a as) (Cons b bs)
\end{verbatim}}

>>>>

STG supports pattern matching but only in a simple form and only in
\texttt{case} expressions.  Mini-Haskell extends this to something approaching
what is found in Haskell.  Functions, including lambda expressions, may match on
all their arguments. Named functions may have multiple definitions to exhaust
the combinations of patterns in their arguments, and patterns in all contexts
(functions and case expressions) may be nested arbitrarily deep.  This feature
greatly simplifies the task of defining more complex behavior.  Without it,
each matched parameter of a function requires an additional level of nested
\texttt{case} expressions. The same is true of each level of nesting within a
single pattern.
%
Even relatively simple functions can be painful to write, such as \texttt{unzip}:
{\footnotesize
\begin{verbatim}
   unzip = FUN(list -> 
     case list of s1 { Nil -> let {res = CON( Pair nil nil)} in res;
                    Cons x xs -> case x of s2 {
                      Pair a b -> case unzip xs of s3 {
                        Pair as bs -> let {aas = CON(Cons a as);
                                           bbs = CON(Cons b bs);
                                           res = CON(Pair aas bbs)}
                                      in res }}})
\end{verbatim}}
\noindent In mini-Haskell this becomes
{\footnotesize
\begin{verbatim}
   unzip :: List (Pair a b) -> Pair (List a) (List b)
   unzip Nil = Pair Nil Nil
   unzip (Cons (Pair a b) xs) =
     case unzip xs of
       TP2 as bs -> Pair (Cons a as) (Cons b bs)
\end{verbatim}}
